The Forward March of Categorical Tolerance in the United States\thanks{Reserved for acknowledgments}

### 2025-06-08 manuscript.tex
Updates from Overleaf

\section*{Results}
\begin{figure}[ht!]
    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
    \centering
     \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/uni-dist-cat-tol-pol.png}
            \caption{Political Ideology}
            \label{fig:cat-tol-pol}
    \end{subfigure}
     \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/uni-dist-cat-tol-edu.png}
            \caption{Education}
            \label{fig:cat-tol-edu}
    \end{subfigure}
     \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/uni-dist-cat-tol-inc.png}
            \caption{Income}
            \label{fig:cat-tol-inc}
    \end{subfigure}
     \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/uni-dist-cat-tol-age.png}
            \caption{Age}
            \label{fig:cat-tol-age}
    \end{subfigure}
     \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/uni-dist-cat-tol-rac.png}
            \caption{Ethnoracial Identification}
            \label{fig:cat-tol-rac}
    \end{subfigure}
     \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/uni-dist-cat-tol-gen.png}
            \caption{Gender Identification}
            \label{fig:cat-tol-gen}
    \end{subfigure}
    \caption{Proportion of Categorical Tolerants across different socio-demographic characteristics.}
    \label{fig:cat-tol}
\end{figure}

>>>>

\section*{Results}
\subsection*{Probability of Dislikes by Genre}
Table~\ref{tab:dis-by-genres} shows the probability of any genre experiencing a judgment of dislike. As we can see, Metal is the genre more likely to be disliked, consistent with previous work in the United States \citep{bryson1996anything-311, lizardo2015musical-8c6}. Electronic Dance Music, Rap/Hip Hop, and Broadway/Musicals are also toward the top in terms of dislikes. R\&B, Rock, and Pop/Top 40, on the other hand, have comparatively low odds of being disliked.

\subsection*{Univariate Distribution of Number of Dislikes}
\begin{figure}[ht!]
        \includegraphics[width=1.0\textwidth]{Tabs/desc-tab-dislike.png}
    \caption{Proportion of dislikes by genre.}
    \label{tab:dis-by-genres}
\end{figure}

\begin{figure}[ht!]
        \includegraphics[width=1.0\textwidth]{Plots/uni-dist-cat-tol.png}
    \caption{Univariate plot of number of dislikes.}
    \label{fig:main}
\end{figure}
Figure~\ref{fig:main} shows the univariate distribution of the number of dislikes for the LM 2025 data. As we can see, the distribution exhibits excess zeroes, with about 20\% of the sample reporting zero dislikes among the twelve musical genres included.

\begin{figure}[ht!]
    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
    \centering
     \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/uni-dist-cat-tol-pol.png}
            \caption{Political Ideology}
            \label{fig:cat-tol-pol}
    \end{subfigure}
     \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/uni-dist-cat-tol-edu.png}
            \caption{Education}
            \label{fig:cat-tol-edu}
    \end{subfigure}
     \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/uni-dist-cat-tol-inc.png}
            \caption{Income}
            \label{fig:cat-tol-inc}
    \end{subfigure}
     \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/uni-dist-cat-tol-age.png}
            \caption{Age}
            \label{fig:cat-tol-age}
    \end{subfigure}
     \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/uni-dist-cat-tol-rac.png}
            \caption{Ethnoracial Identification}
            \label{fig:cat-tol-rac}
    \end{subfigure}
     \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Plots/uni-dist-cat-tol-gen.png}
            \caption{Gender Identification}
            \label{fig:cat-tol-gen}
    \end{subfigure}
    \caption{Proportion of Categorical Tolerants across different socio-demographic characteristics.}
    \label{fig:cat-tol}
\end{figure}
